### 2014-10-08 editaveis/sistema_ambiente.tex
Show the code with nice view

\begin{lstlisting}[language=Python,caption={Trecho do código principal}]

def main():
    pid_bikex = sys.argv[1:2]
    print "Father: %s" % pid_bikex
    print "Mine: %d " % getpid()
    print SIG1,SIG2,SIG3
    msp430.curb = sensor.Break(msp430.serial,0)
    msp430.passives = sensor.Passives(msp430.serial,0)

>>>>

\begin{lstlisting}[language=Python,caption={Trecho do código principal}]
def main():
    pid_bikex = sys.argv[1:2]
    print "Father: %s" % pid_bikex
    print "Mine: %d " % getpid()
    print SIG1,SIG2,SIG3
    msp430.curb = sensor.Break(msp430.serial,0)
    msp430.passives = sensor.Passives(msp430.serial,0)
